The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
update refs and cleanup workshop sentence

Perhaps in recognition of the general desire to improve rates software citation, a number of workshops specifically aimed at addressing issues around software citation have been hosted (and sponsored) by funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) (~\cite{swdatacite}, ~\cite{ssisoftwarecredit}, ~\cite{aas-software-index}, ~\cite{saga}, ).

\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}

>>>>

In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) have hosted (and sponsored) a number of workshops specifically aimed at addressing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
